Memristor-based recurrent modules for neural computing

### 2023-10-31 paper/dataset.tex
Rearranged figures
Raccourci

\begin{figure}[h]
  \centering
  \includesvg[width=\columnwidth,pretex=\scriptsize]{datasets/airline}
  \caption{The airline dataset. The vertical lines represent a full year.}
  \label{graph:airline}
\end{figure}

@@

This dataset is far more interesting and complex than the latter. This data set aims to use \acp{LSTM} to mimic the behavior of real neurons. As explained in \cite{celegans}, Caenorhabditis elegans are simple organisms that are getting very popular for whole brain organization studies. The point of this problem is to reproduce the nervous system of the \ac{C. elegans}. This is done using recorded data of the input of 4 neurons and the output of 4 other neurons.

@@

>>>>

\begin{figure}[b]
  \centering
  \includesvg[width=\columnwidth,pretex=\scriptsize]{datasets/airline}
  \caption{The airline dataset. The vertical lines represent a full year.}
  \label{graph:airline}
\end{figure}

@@

This dataset is far more interesting and complex than the latter. This data set aims to use \acp{LSTM} to mimic the behavior of real neurons. As explained in \cite{celegans}, Caenorhabditis elegans (C. elegans)  are simple organisms that are getting very popular for whole brain organization studies. The point of this problem is to reproduce the nervous system of the \ac{C. elegans}. This is done using recorded data of the input of 4 neurons and the output of 4 other neurons.

@@

An example of an input/output sequence is shown in \cref{graph:celegansAnalog1} along with the digital and analog predictions.
